Supporting Information for ``Nonparametric Block Bootstrap Kolmogorov--Smirnov Goodness-of-Fit Test''

### 2024-08-18 manuscript/supplement.tex
hat theta_0
minor comments on notation
an  attempt to complete the proof of proposition 2

\begin{proof}[Proof of Proposition~2]
  We want to show that
  \jy{What is $\hat\theta_0$? Should it be $\hat\theta_n$?}
\begin{align}\label{eq-con-boot}
\begin{pmatrix}
G_n^{(b)}(x)  \\ 
\sqrt{n}(F(x;\hat{\theta}_n^{(b)})-F(x;\hat{\theta}_0))
\end{pmatrix}\Rightarrow^{*}
\begin{pmatrix}
G_{\infty}(x) \\
f(x;\theta_0)U
\end{pmatrix}
\end{align}
where $\Rightarrow^*$ means convergence in distribution almost surely and 
$\hat{\theta}_0:=\mathbb{E}^{(b)}[\hat{\theta}_n^{(b)}]$. 
In the bootstrap world, we have an expansion similar to (\ref{eq-expan}):
\begin{align*}
\hat{\theta}_n^{(b)}-\hat{\theta}_0 = \frac{1}{n}\sum^{n}_{i=1}h(X_i^{(b)};
\hat{\theta}_0) + \frac{1}{\sqrt{n}}R_n^{(b)},    
\end{align*}
where $R_n^{(b)} \overset{p^*}{\rightarrow} 0$, where 
$\overset{p^*}{\rightarrow}$ means convergence in probability almost surely. 
Note that 
\begin{align*}
\mathbb{E}^{(b)}\left[\frac{1}{n}\sum^{n}_{i=1}h(X_i^{(b)};
\hat{\theta}_0)\right]
=&\frac{1}{n}\sum^{k}_{j=1}\mathbb{E}^{(b)}\left[\sum^{S_j+l-1}_{i=S_j}h(X_{i};
\hat{\theta}_0)\right]
\\=&\frac{k}{n^2}[\sum^{n - l + 1}_{j=1}\sum^{j+l-1}_{i=j}h(X_{i};
\hat{\theta}_0) +
\sum^{n}_{j=n - l + 2}[\sum^{n}_{i=j}h(X_{i};\hat{\theta}_0) +
\sum^{j - n + l -1}_{i=1}h(X_{i};\hat{\theta}_0)]]
\\=&\frac{k}{n^2}\sum^{n}_{i=1}l h(X_{i};\hat{\theta}_0).
\end{align*}

@@

>>>>

\begin{proof}[Proof of Proposition~2]
  We want to show that
\begin{align}\label{eq-con-boot}
\begin{pmatrix}
G_n^{(b)}(x)  \\ 
\sqrt{n}(F(x;\hat{\theta}_n^{(b)})-F(x;\hat{\theta}_0))
\end{pmatrix}\Rightarrow^{*}
\begin{pmatrix}
G_{\infty}(x) \\
f(x;\theta_0)U
\end{pmatrix}
\end{align}
where $\Rightarrow^*$ means convergence in distribution almost surely and 
$\hat{\theta}_0:=\mathbb{E}^{(b)}[\hat{\theta}_n^{(b)}]$. 
In the bootstrap world, we have an expansion similar to (\ref{eq-expan}):
\begin{align*}
\hat{\theta}_n^{(b)}-\hat{\theta}_0 = \frac{1}{n}\sum^{n}_{i=1}h(X_i^{(b)};
\hat{\theta}_0) + \frac{1}{\sqrt{n}}R_n^{(b)},    
\end{align*}
where $R_n^{(b)} \overset{p^*}{\rightarrow} 0$, where 
$\overset{p^*}{\rightarrow}$ means convergence in probability almost surely. 
Note that 
\begin{align*}
\mathbb{E}^{(b)}\left[\frac{1}{n}\sum^{n}_{i=1}h(X_i^{(b)};
\hat{\theta}_0)\right]
=&\frac{1}{n}\sum^{k}_{j=1}\mathbb{E}^{(b)}\left[\sum^{S_j+l-1}_{i=S_j}h(X_{i};
\hat{\theta}_0)\right]
\\=&\frac{k}{n^2}[\sum^{n - l + 1}_{j=1}\sum^{j+l-1}_{i=j}h(X_{i};
\hat{\theta}_0) +
\sum^{n}_{j=n - l + 2}[\sum^{n}_{i=j}h(X_{i};\hat{\theta}_0) +
\sum^{j - n + l -1}_{i=1}h(X_{i};\hat{\theta}_0)]]
\\=&\frac{k}{n^2}\sum^{n}_{i=1}l h(X_{i};\hat{\theta}_0).
\end{align*}

@@

To establish tightness, we need to demonstrate that for any \(\epsilon > 0\),
\[
\lim_{\delta \to 0} \limsup_{n \to \infty} \mathbb{P}^*\left( \sup_{|x - y| < \delta} |G_n^{(b)}(x) - G_n^{(b)}(y)| \geq \epsilon \right) = 0.
\]

Consider the difference
\[
G_n^{(b)}(x) - G_n^{(b)}(y) = \sqrt{n} \left( F_n^{(b)}(x) - F_n^{(b)}(y) - (F_n(x) - F_n(y)) \right).
\]
This difference can be further decomposed as
\[
G_n^{(b)}(x) - G_n^{(b)}(y) = \sqrt{n} \left( \frac{1}{n} \sum_{i=1}^n \left[ 1\{X_i^{(b)} \leq x\} - 1\{X_i^{(b)} \leq y\} \right] - (F(x) - F(y)) \right).
\]

Given that \(F(x)\) is continuous, and using the fact that bootstrap
samples maintain the mixing properties of the original data (Politis,
Romano, and Wolf, 1999), we can apply a concentration inequality such
as Hoeffding's inequality to the bootstrap samples. This yields that
for any small \(\delta > 0\),
\[
\mathbb{P}^*\left( \sup_{|x - y| < \delta} |G_n^{(b)}(x) - G_n^{(b)}(y)| \geq \epsilon \right) \leq 2 \exp\left( -2n \epsilon^2 \right).
\]
Taking the limit as \(\delta \to 0\) and \(n \to \infty\), we conclude that
\[
\lim_{\delta \to 0} \limsup_{n \to \infty} \mathbb{P}^*\left( \sup_{|x - y| < \delta} |G_n^{(b)}(x) - G_n^{(b)}(y)| \geq \epsilon \right) = 0,
\]
which establishes tightness for \(G_n^{(b)}(x)\).

\bigskip

Given the finite-dimensional convergence and tightness established
above, by the continuous mapping theorem, we have
\[
T_n^{(b)} = \sup_x \left| G_n^{(b)}(x) + f(x; \theta_0) U \right| \Rightarrow^* \sup_x \left| G_\infty(x) + f(x; \theta_0) U \right|,
\]
completing the proof.
